Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-27 Corrected_version.tex
change thomas

Provided that the initial data is smooth, the initialization gives us 
\begin{equation}\label{init_1D}
 \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C_0 h\eps .
\end{equation}

@@

\begin{proposition} \label{heqtode}
There exists a constant which depend of the time such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
 \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $v=-\frac{\varepsilon}\sigma \partial_x p$ with $p$ the diffusion solution of (\ref{difffff}) and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p +\frac{1}{\eps}\partial_{x}v=0,\\
\partial_t v+ \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}v = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt v=-\frac{\varepsilon}\sigma \partial_{tx} p=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=v-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

\begin{eqnarray} \label{eq:eqn1}

@@

)^2\right ) \bigg) \\

@@

\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2.

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
\begin{proposition}\label{ds1d}
Under assumption \ref{geometrie1d}, the following estimate holds
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
h 
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
\right)  \bigg(  
e^{T/2\sigma} + 
\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) } \bigg).
\end{equation*}
\end{proposition}

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \|p_0\|_{H^2(\mathbb{R})} \bigg) ,

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )} \|p_0\|_{H^2(\mathbb{R})} \big)$. 

@@

\begin{theorem} \label{theor:1d}
Assuming a sufficiently smooth well prepared initial data,
the scheme $P_h^\eps$ converges to $P^\eps$ at order at least 
$\frac13$ in $L^2([0,T]\times \mathbb{R}   )$, uniformly with respect to $\eps$
\end{theorem}
\begin{proof}
All the previous estimates
show that (\ref{eq:mod3}-\ref{eq:mod4})  are true
with
$a=1$, $b=c=\frac12$ and $d=1$.
Moreover $\|P_h^\varepsilon-P_h^0  \|\leq C(T) \eps $
by proposition (\ref{gttods}) which means this term has the same
scaling as $\|P^\varepsilon-P^0  \|\approx C(T) \eps$.
So it can be  incorporated 
in  estimate (\ref{eq:mod3}) with $a=1$.
Using the general
method described at the beginning of this work in proposition \ref{prop:1}, 
one  obtains the convergence
estimate of convergence
$
\|\mathbf V_h^\eps -\mathbf V^\eps   \|_{L^2([0,T]\times \mathbb{R}   )  }
\leq C(T) h^{ q }
$
with the order of convergence
$
q=\frac{ac}{a+b}=\frac13$.
\end{proof} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{proposition}\label{heqtode2d}
The error between the two solutions
can be  upper bounded by
\begin{equation}\label{ine3}
\textcolor{red}{\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
\| \mathbf{v} 
 \|_{   L^\infty([0,T]; H^n(\Omega))  }
 \leq
C \eps
\|p_0 \|_{H^{3+n}(\Omega)},
\qquad n \in \mathbb N.}
\end{equation}
\end{proposition}
\begin{proof}
The structure of the 
proof in the $L^\infty( [0,T];L^2(\Omega))$ norm is the same as the one
of proposition \ref{heqtode}.
Since the coefficients of the problem are constant, similar bounds are obtained
at any order of derivation which proves the estimate for any $n>0$.
\end{proof}

@@

\begin{pro}
Consider a smooth enough initial $p_0$.
One has
\begin{equation*} \label{eq:der1}
\bigg\|  \frac{d}{dt} p_h  \bigg\|_{ L^\infty([0,T];L^2(\Omega)   )  }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right),  
\end{equation*}
and
\begin{equation}\label{e:qder2}
\bigg\|( \frac{d}{dt} \mathbf u_r  )_r \bigg\|_{L^2([0,T] \times  \Omega)   }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right).
\end{equation}
\end{pro}
\begin{proof}
Let us denote the time derivative of any $f$
as $\tilde f=\partial_t f$.
By linearity of the system (\ref{das:1}), one has
\begin{equation*}\label{das:1:der}
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid \frac{d}{dt} \tilde p_{j}+
\sum_{r}(l_{jr}  \tilde\uu_r,\njr)=0\\
 \sum_{r}l_{jr} (\njr, \tilde\uu_r - \tilde\uu_j)\njr=0\\
 \left( \eps\sum_{j}\alj+  \sigma B_r\right) \tilde\uu_r=
\sum_{j}\ljr  \tilde p_j\njr+\eps\sum_j\alj \tilde\uu_j
\end{array}
\right.
\end{equation*}
The $L^2$ stability property yields
$$
\|  \tilde p_h(t)\|^2_{L^\infty([0,T];L^2(\Omega)  )   } 
+\int_0^t \sum_r ( B_r \tilde\uu_r, \tilde\uu_r )dt
\leq
\|  \tilde p(0)\|_{L^2(\Omega)} 
$$
where this last quantity can be estimated
with the first equation of (\ref{das:1}):
the square of the norm in (\ref{e:qder2}) is also bounded by
the same quantity.
 It remains to bound $\|  \tilde p(0)\|_{L^2(\Omega)  )  } $.
At $t=0$ one has 
$$
\frac{d}{dt} p_j=\frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \nabla p(\x_r) ,\njr)
- \frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \mathbf q_r ,\njr).
$$
Using the same consistency arguments as before, the first
term in the right hand side is bounded in $L^2$ uniformly
with respect to $h$ and $\eps$. The second one is bounded in $L^2$ 
by a term of order 
$C\frac{h \sqrt {\max( h^2, \eps h)}}{h^2}=C
\max\left(1,\sqrt{\frac{\eps} {h} }
\right)$. The proof is ended.
\end{proof}

>>>>

Provided that the initial data is smooth, the initialization gives us 
\begin{equation}\label{init_1D}
 \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C_0 h\eps \|p_0\|_{H^2(\mathbb{R})}.
\end{equation}

@@

\begin{proposition} \label{heqtode}
There exists a constant which depend of the time such that 
\begin{equation}\label{esti_p_eps_p_0}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
 \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation}
\end{proposition}
\begin{proof}
We define $v=-\frac{\varepsilon}\sigma \partial_x p$ with $p$ the diffusion solution of (\ref{difffff}) and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p +\frac{1}{\eps}\partial_{x}v=0,\\
\partial_t v+ \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}v = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt v=-\frac{\varepsilon}\sigma \partial_{tx} p=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=v-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{equation}\label{esti_naive_1d}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}_0
\right\|_{H^1(\mathbb{R})}.
\end{equation}

@@

\begin{eqnarray} 

@@

)^2\right ) \bigg)\label{eq:eqn1} \\

@@

\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2.\label{eq:eqn2}

@@

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn2}) can be bounded using the Jensen inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
\begin{proposition}\label{ds1d}
Under assumption \ref{geometrie1d}, the following estimate holds
\begin{equation}\label{esti_p_h_0_p_0}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
h 
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
\right)  \bigg(  
e^{T/2\sigma} + 
\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) } \bigg).
\end{equation}
\end{proposition}

@@

\begin{equation}\label{p_h_eps_p_h_0_1d}
\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb R)} \leq  \eps e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) } \bigg)  \|p_0\|_{H^2(\mathbb{R})},

@@

\|\V_h^{\eps}-\W^\eps_h\|_{L^2([0,T]\times\mathbb{R})} \leq \eps e^{T/2} \big(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } ( \frac12 + \frac{1}{\sigma^2} )}  \big) \|p_0\|_{H^2(\mathbb{R})} $.  

@@

\begin{theorem} \label{theor:1d}
Assuming a sufficiently smooth well prepared initial data,
the scheme $P_h^\eps$ converges to $P^\eps$ at order at least 
$\frac13$ in $L^2([0,T]\times \mathbb{R}   )$, uniformly with respect to $\eps$
\end{theorem}
\begin{proof}
All the previous estimates
show that (\ref{eq:mod3}-\ref{eq:mod4})  are true
with
$a=1$, $b=c=\frac12$ and $d=1$.
Moreover $\|P_h^\varepsilon-P_h^0  \|\leq C(T) \eps $
by proposition (\ref{gttods}) which means this term has the same
scaling as $\|P^\varepsilon-P^0  \|\approx C(T) \eps$.
So it can be  incorporated 
in  estimate (\ref{eq:mod3}) with $a=1$.
Using the general
method described at the beginning of this work in proposition \ref{prop:1}, 
one  obtains the convergence
estimate of convergence
$
\|\mathbf V_h^\eps -\mathbf V^\eps   \|_{L^2([0,T]\times \mathbb{R}   )  }
\leq C(T) h^{ q }
$
with the order of convergence
$
q=\frac{ac}{a+b}=\frac13$.
\end{proof} 
~~\\
\begin{proof}[ALTERNATIVE PROOF]~~\\
\\
All the previous estimates
show that (\ref{eq:mod3}-\ref{eq:mod4})  are true
with
$a=1$, $b=c=\frac12$ and $d=1$. More specifically, estimates \eqref{esti_naive_1d}, \eqref{p_h_eps_p_h_0_1d}, \eqref{esti_p_h_0_p_0} and \eqref{esti_p_eps_p_0} shows that
\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C \min\bigg( \sqrt \frac{h}\eps  \: , \: \eps + h + \eps \bigg)
\end{equation*}
where
\begin{equation*}
\begin{aligned}
C =  2 \max \bigg\{  & \sqrt{h\eps + 2T + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\left\| \V^{\eps}_0
\right\|_{H^1(\mathbb{R})} \: ,  \\
&\|p_0\|_{H^3(\mathbb{R})} \max\bigg( e^{T/2} \bigg(  C_0h + \sqrt{ \frac{1}{\sigma C_{\mathcal{M}} } \big( \frac12 + \frac{1}{\sigma^2} \big) }  \bigg) \: ,\\
& \hspace{3cm} e^{T/2\sigma} + 
\eps \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }  \: ,  \frac{T}{\sigma^2}  \bigg) \bigg\} .
\end{aligned}
\end{equation*}
Using the general
method described at the beginning of this work in proposition \ref{prop:1}, 
one  obtains the convergence
estimate of convergence
$
\|\mathbf V_h^\eps -\mathbf V^\eps   \|_{L^2([0,T]\times \mathbb{R}   )  }
\leq C(T) h^{ q }
$
with the order of convergence
$
q=\frac{ac}{a+b}=\frac13$.

@@

\begin{proposition}\label{heqtode2d}
The error between the two solutions
can be  upper bounded by
\begin{equation}\label{ine3}
\| p^\epsilon-p\|_{   L^\infty([0,T];H^n(\Omega))  }+
\| \mathbf{v} 
 \|_{   L^\infty([0,T]; H^n(\Omega))  }
 \leq
\frac{T}{\sigma^2} \eps
\|p_0 \|_{H^{3+n}(\Omega)},
\qquad n \in \mathbb N.
\end{equation}
\end{proposition}
\begin{proof}
The structure of the 
proof in the $L^\infty( [0,T];L^2(\Omega))$ norm is the same as the one
of proposition \ref{heqtode}.
Since the coefficients of the problem are constant, similar bounds are obtained
at any order of derivation which proves the estimate for any $n>0$.
\end{proof}

@@

\begin{pro}
Consider a smooth enough initial $p_0$.
One has
\begin{equation*} \label{eq:der1}
\bigg\|  \frac{d}{dt} p_h  \bigg\|_{ L^\infty([0,T];L^2(\Omega)   )  }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right),  
\end{equation*}
and
\begin{equation}\label{e:qder2}
\bigg\|( \frac{d}{dt} \mathbf u_r  )_r \bigg\|_{L^2([0,T] \times  \Omega)   }
\leq C \max\left(1,\sqrt{\frac{\eps} {h} }
\right).
\end{equation}
\end{pro}
\begin{proof}
Let us denote the time derivative of any $f$
as $\tilde f=\partial_t f$.
By linearity of the system (\ref{das:1}), one has
\begin{equation*}\label{das:1:der}
\left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid \frac{d}{dt} \tilde p_{j}+
\sum_{r}(l_{jr}  \tilde\uu_r,\njr)=0\\
 \sum_{r}l_{jr} (\njr, \tilde\uu_r - \tilde\uu_j)\njr=0\\
 \left( \eps\sum_{j}\alj+  \sigma B_r\right) \tilde\uu_r=
\sum_{j}\ljr  \tilde p_j\njr+\eps\sum_j\alj \tilde\uu_j
\end{array}
\right.
\end{equation*}
The $L^2$ stability property yields
$$
\|  \tilde p_h(t)\|^2_{L^\infty([0,T];L^2(\Omega)  )   } 
+\int_0^t \sum_r ( B_r \tilde\uu_r, \tilde\uu_r )dt
\leq
\|  \tilde p(0)\|_{L^2(\Omega)}^2
$$
where this last quantity can be estimated
with the first equation of (\ref{das:1}):
the square of the norm in (\ref{e:qder2}) is also bounded by
the same quantity.
 It remains to bound $\|  \tilde p(0)\|_{L^2(\Omega)  )  } $.
At $t=0$ one has 
$$
\frac{d}{dt} p_j=\frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \nabla p(\x_r) ,\njr)
- \frac1\sigma \frac1{|\Omega_j|}
\sum_r l_{jr}  ( \mathbf q_r ,\njr).
$$
Using the same consistency arguments as before, the first
term in the right hand side is bounded in $L^2$ uniformly
with respect to $h$ and $\eps$. The second one is bounded in $L^2$ 
by a term of order 
$C\frac{h \sqrt {\max( h^2, \eps h)}}{h^2}=C
\max\left(1,\sqrt{\frac{\eps} {h} }
\right)$. The proof is ended.
\end{proof}
